Scalar on Function Regression \\ with Applications to Near-Infrared Spectroscopy

### 2022-01-15 Presentation/slides.tex
Slides - Meeting

	% I'm not really a fan of a table of contents in short presentations (Jakob)
	% Outline frame
	%\begin{frame}{Outline}
	%	\tableofcontents
	%\end{frame}

@@

		\begin{itemize}
			\item Continuous underlying process where $x_i(t)$ exists $\forall t \in [T_1, T_2]$ but is only observed at $x_{i}(t_{j,i})$
			\item Regression to determine relationship between octane rating and spectral curves
		\end{itemize}

@@

	%\begin{frame}{Theory}
	%	A simple functional dataset is given by 
	%	
	%	
	%	\begin{itemize}
	%		\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
	%		\item Only observed at $x_{i}(t_{j,i})$
	%		\item Example: Gasoline dataset (60 x 400)
	%		\item Other Examples: Growth curves, financial data, human perception (pitch), ...
	%	\end{itemize}
	%\end{frame}

@@

	%\begin{frame}{Random Function}
	%	The realization of random function can be described as
	%	$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
	%	where $\mathbb{E}$ is the index set and $X(t, \cdot)$ is
	%	$\mathcal{F}$-measurable function on the sample space $\Omega$.\\
	%	\begin{itemize}
	%		\item It can be shortened to $X(t)$ by omitting $\omega$ or I can
	%		be written as $X(t)(\omega)$.
	%		\item The function is realized when the $X(t)$ exists $\forall t
	%		\in \mathbb{E}$.
	%	\end{itemize}
	%\end{frame}

@@

		$$x_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx
		\sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in
		\mathbb{E}$$

		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion
		and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$
		to:
		\vspace{0.2cm}

		\begin{itemize}
			\item make the function smoother
			\item replace the original curves $x_{i}(t)$ with a smaller
			collection of $c_{nm}$
		\end{itemize}     
	\end{frame}

@@

	\begin{frame}{Basis Functions}
		\textbf{B-spline Basis Functions} are polynomial functions defined by
		an order and a set of knots.
		\begin{figure}
			\includegraphics[width =
			\textwidth]{../Graphics/Bspline_Basis.pdf}
			%\caption {Bspline basis functions}
		\end{figure}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		How do we choose the number $K$ of basis functions?

@@

		\begin{itemize}
			\item The larger $K$, the better the fit to the data, but also more fitting noise
			\item If $K$ is too small, the expansion would miss some significant information
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		Truncating the functional basis allows us to estimate coefficients using \textbf{Multivariate Regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an approximated coefficient function $\hat{\beta}(t)$:
		\vspace{-0.2cm}
		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{c}_{L,j} \phi_j(t)$$

		This is dependent on...\vspace{-0.2cm}
		\begin{multicols}{2}
			\begin{itemize}
				\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
				\item The truncation parameter $L$\vfill\null
				\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the observations
				\item The truncation parameter for the observations $K$
			\end{itemize}
		\end{multicols}

@@

		\begin{itemize}
    		\item Four combinations with different number of cubic basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP, ...)

@@

	\begin{frame}{Simulation - Interpretation of results}\label{Results}
		\textbf{Basis Expansion Regression}
		\begin{itemize}
    			\item Smooth true coefficient functions requires smaller number of $n_{basis}$ and vice versa
    			\item Setup with higher noise requires smoother function.
    			\item  Bspline setup performs overall a bit better.
		\end{itemize}

@@

	\begin{frame}{Application setup}
		\begin{itemize}
			\item Use insights from the simulation study to uncover dependence.
			\item Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
			\item Validation set approach:	Scores of test data needs to be estimated by the training data. 
			\item Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}

	%\begin{frame}{Summary}
	%	\begin{itemize}
	%	\item
    %		Concepts of functional data: 
    %		\begin{itemize}
	%		\item See dataset as smooth curve than as set of discrete measurements.
    %			\item Theory of Random Functions, motivated from random variable.
    %			\item Basis expansion and its Bias-Variance tradeoff.
    %			\item Scalar on Function Regression via Basis Expansion.
    %			\item Functional principal component Analysis and FPCR.
	%	\end{itemize}
    %		\item
    %		Simulation study results: specification depends on function and signal-to-noise ratio
    %		\item
    		% Guided you  from the beginning to the end of the presentaion through one application ....
    %		Guided through application to predict octane ratings.

	%	\end{itemize}
	%\end{frame}

>>>>

@@

		\begin{itemize}
			\item Continuous underlying process where $x_i(t)$ exists $\forall t \in [T_1, T_2]$ but is only observed at $t_{j,i}$
			\item Regression to determine relationship between octane rating and spectral curves
		\end{itemize}

@@

@@

@@

		$$x_{i}(t) = \sum_{j \in \mathcal{I}} c_{i,j}\phi_{j}(t) \approx
		\sum_{j=1}^{L} c_{i, j}\phi_{j}(t), \quad i = 1, \dots, n, \quad \forall t \in
		\mathbb{E}$$

		where $\phi_{j}(t)$ is the $j^{th}$ basis function of the expansion
		and $c_{i, j}$ is the corresponding coefficient. We truncate the basis at $L$
		to:
		\vspace{0.2cm}

		\begin{itemize}
			\item make the function smoother
			\item replace the original curves $x_{i}(t)$ with a smaller
			collection of $c_{n, m}$
		\end{itemize}     
	\end{frame}

@@

	\begin{frame}{Basis Functions}
		\textbf{B-spline Basis Functions} are piece-wise polynomial functions defined by
		an order and a set of knots.
		\begin{figure}
			\includegraphics[width =
			\textwidth]{../Graphics/Bspline_Basis.pdf}
			%\caption {Bspline basis functions}
		\end{figure}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		How do we choose the number $L$ of basis functions?

@@

		\begin{itemize}
			\item The larger $L$, the better the fit to the data, but also more fitting noise
			\item If $L$ is too small, the expansion would miss some significant information
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		Truncating the functional basis allows us to estimate coefficients using \textbf{Multivariate Regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an estimated coefficient function $\hat{\beta}_L(t)$:
		\vspace{-0.2cm}
		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{c}_{L,j} \phi_j(t)$$

		This is dependent on...\vspace{-0.2cm}
		\begin{multicols}{2}
			\begin{itemize}
				\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
				\item The truncation parameter $L$\vfill\null
				\item The basis $(\psi_j(t))_{j \in \mathcal{L}}$ used for the observations
				\item The truncation parameter for the observations $K$
			\end{itemize}
		\end{multicols}

@@

		\begin{itemize}
    		\item Four combinations with different number of cubic bspline basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP, ...)

@@

	\begin{frame}{Simulation - Interpretation of Results}\label{Results}
		\textbf{Basis Expansion Regression}
		\begin{itemize}
    			\item Smooth true coefficient functions requires smaller number of $n_{basis}$ and vice versa
    			\item Setup with higher noise requires smoother function.
    			\item  Bspline setup performs overall a bit better.
		\end{itemize}

@@

	\begin{frame}{Application Setup}
		\begin{itemize}
			\item Use insights from the simulation study to uncover dependence.
			\item Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
			\item Validation set approach:	Scores of test data needs to be estimated by the training data. 
			\item Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}
